## Process Baseline Corridor Charging Availability 
# Author: Catherine Ledna & Lily Hanig
# Date: 08/05/2022

#
### National Highway system
# https://www.fhwa.dot.gov/planning/national_highway_system/nhs_maps/

### Alternative Fuel Corridors 
# https://hepgis.fhwa.dot.gov/fhwagis/ViewMap.aspx?map=Highway+Information|Electric+Vehicle+(EV-Round+1,2,3,4,5+and+6)#

### EV stations
# https://afdc.energy.gov/stations/#/analyze?fuel=ELEC&status=E&status=P

### disadvantaged communities shapefile DOT
# https://www.transportation.gov/equity-Justice40

# Population centers 
# https://www2.census.gov/geo/docs/reference/cenpop2020/county/CenPop2020_Mean_CO.txt

### Libraries and parameters

```{r}
library(sf)
library(rgdal)
library(data.table)
library(dplyr)
library(igraph)
library(here)
library(beepr)
library(tidyverse)
library(lwgeom)

all.chargers.flag <- FALSE # if this is set to FALSE, it excludes TESLA
segment.dist <- 50 # miles
# Range distance if set to NA considers the whole contiguous US
range.dist <- 500 # miles 
short.road.exclusion <- 10 # miles
meters.per.mile <- 1609.34
data.processing <- F
options(dplyr.summarise.inform = FALSE)

```

### File Path locations
```{r}

  proj.contig <- 5070 # 4326 # 
  proj.isl <- 5070
  proj.ak <- 3338
  
  
  net.file <- "nhs20221230/NHS_20221230.shp"                        #"nhs20210815/National_NHS_2021-08-23.shp"
  afc.net.file <- "AltFuels_Rounds1-6_2022-07-26/AltFuels_Rounds1-6_2022-07-26.shp"
  alt.fuel.stations <- "alt_fuel_stations_3_1_2023.csv"             #"alt_fuel_stations_10_17_2022.csv"
  DAC.file <- "shapefiles/DOT_DAC/DOT_Disadvantage_Layer_Final_April2022.shp"
  net.folder <- "nhs2019"
  county.file <- "tl_2020_us_county/tl_2020_us_county.shp"
  county.pop.center.file <- "CenPop2020_Mean_CO.csv"
  county.center.file <- "2020_us_population_center_county.csv"
  file.path <- here("data/")                                         #here("Research/EV_NREL/data/")
  folder.name <- here("data/shapefiles/")
  state.file <- "tl_2022_us_state/tl_2022_us_state.shp"

```

### function found from internet to split geometric line strings (above 50 miles)
```{r}
split_lines <- function(input_lines, id = "ID",max_length = 10*meters.per.mile) {
  #input_lines <- hwys.test
  #id <- 'SIGN1'
  
  if(max_length < 50) warning("short max length detected, do you have your units right?")
  
  geom_column <- attr(input_lines, "sf_column")
  
  input_crs <- sf::st_crs(proj.contig)
  
  input_lines["geom_len"] <- sf::st_length(input_lines[[geom_column]])
  input_lines["geom_id"] <- 1:nrow(input_lines)
  
  attr(input_lines[["geom_len"]], "units") <- NULL
  input_lines[["geom_len"]] <- as.numeric(input_lines[["geom_len"]])
  
  too_long <- input_lines %>% filter(geom_len >= max_length)
  short_lines <- input_lines %>% 
                 filter(geom_len < max_length) %>% 
                 mutate(split_fID = 1) %>% select(-geom_len)
  rm(input_lines) # just to control memory usage in case this is big.
  print(nrow(too_long))
  too_long <- too_long %>%
              mutate(pieces = ceiling(geom_len / max_length)) %>% # ceiling
              select(-geom_len)
  if (nrow(too_long) != 0){
    too_long$fID <- 1:nrow(too_long)
    split_points <- sf::st_drop_geometry(too_long)[rep(seq_len(nrow(too_long)), too_long[["pieces"]]),] %>%
      select(-pieces)
  
    split_points <- split_points %>% group_by(SIGN1) %>%
      mutate(split_fID = row_number()) %>%
      group_by(fID) %>%
      mutate(piece = 1:n()) %>%
      mutate(start = (piece - 1) / n(),
             end = piece / n()) %>%
      ungroup()
    
    new_line <- function(i, f, t) {
      lwgeom::st_linesubstring(x = too_long[[geom_column]][i], from = f, to = t)[[1]]
    }
    
    split_lines <- apply(split_points[c("fID", "start", "end")], 1,
                         function(x) new_line(i = x[["fID"]], f = x[["start"]], t = x[["end"]]))
    
    rm(too_long)
    #
    split_lines <- st_sf(split_points[c(id, "STFIPS", "CTFIPS", "AADT", "LENGTH", "split_fID", "geom_id")], crs = input_crs, geometry = st_sfc(split_lines, crs = input_crs))
  }

  all_lines <- rbind(short_lines, split_lines) %>% 
    arrange(id, STFIPS, geom_id, split_fID) %>% select(-geom_id) %>%
    st_sf(crs = input_crs)
  return(all_lines)
}
```

### The data processing part, only need to do once, than can switch data.processing to False
```{r}
if (data.processing){

# national highway system

  net <- read_sf(paste0(folder.name, net.file))
  net <- st_transform(net, crs = st_crs(proj.contig))

  hwys.contig <- net # %>% filter(!(STFIPS %in% c(2, 60, 66, 69, 72, 78, 15))) 
  hwys.contig <- st_transform(hwys.contig, crs=st_crs(proj.contig)) #projecting to continent

## AFDC Corridor Points Data (Non-Tesla, meeting criteria)

# Existing stations

  afdc.dcfc <- fread(paste0(file.path, alt.fuel.stations)) %>%
               select(`Fuel Type Code`, `State`, `ZIP`,`Status Code`, `Expected Date`, `EV DC Fast Count`,
                      `Geocode Status`, `Latitude`, `Longitude`, `ID`, `Open Date`, `Country`, `EV Connector Types`)%>%
              # filter(!(is.na(`EV DC Fast Count`)),`EV DC Fast Count` > 0) %>%
               mutate(`Open_Date`=as.character(`Open Date`),
                      `Lat` = `Latitude`,
                      `long` = `Longitude`,
                      `EV DC Fast Count` = ifelse(is.na(`EV DC Fast Count`), 0, `EV DC Fast Count`),
                      `Open_Year` = as.numeric(strsplit(`Open_Date`, split = "/", fixed = T)[[1]][1]),
                      `Open_Year` = ifelse(is.na(`Open_Year`), 2022, Open_Year),
                      `Tesla` = grepl('TESLA', `EV Connector Types`),
                      `NEVI_count` = ifelse(`EV DC Fast Count` >= 4, TRUE, FALSE))
  
  
  afdc.dcfc <- st_as_sf(afdc.dcfc, coords=c("Longitude", "Latitude"), crs=st_crs(4326))
  afdc.dcfc.proj <- st_transform(afdc.dcfc, crs=st_crs(proj.contig)) # filter(!(State %in% c("AK", 'HI', 'PR')))
  
# Trying a new method for unioning the roads and splitting up

  st_precision(hwys.contig) <- 0.1
  hwys.test <- hwys.contig %>%
      group_by(ROUTEID) %>%
      fill(SIGN1) %>% # fills any missing SIGNS with the sign from the other segments with the same ROUTEID 
      mutate(AADT = ifelse(is.na(AADT), mean(AADT), AADT)) %>% # fill in missing AADT with average for that road
      ungroup() %>%
      mutate(LNAME = ifelse(is.na(LNAME), paste0('NA_', row_number()), LNAME),
             ROUTEID = ifelse(is.na(ROUTEID), LNAME, ROUTEID),
             SIGN1 = ifelse(is.na(SIGN1), ROUTEID, SIGN1)) %>%  # replaces any roads with no signs with RouteID
      group_by(SIGN1, STFIPS, CTFIPS) %>%  # group by county and sign name (incase there's the same road name twice in a state)
      summarise(AADT = mean(AADT), 
                geometry = st_union(st_combine(geometry)), # combines road segments into one geometry object
                geometry = st_cast(geometry, "MULTILINESTRING"),
                geometry = st_line_merge(geometry),
                LENGTH = as.numeric(st_length(geometry))/meters.per.mile) %>% # finds length
      ungroup()# total for road
  
  # Roads above (50 miles + short exception) are filtered and chopped up into smaller
  # If a segment is the last one along a road and it's less than 10 miles it gets added to previous segment
  
  hwys.too.long <- hwys.test %>% filter(LENGTH > (segment.dist + short.road.exclusion)) 
  
  hwys.too.long <- lapply(1:nrow(hwys.too.long), function(i) {
      st_cast(hwys.too.long[i, ], "LINESTRING", warn=F, crs = st_crs(proj.contig))
  }) %>% do.call(rbind, .) %>% 
    split_lines(id = "SIGN1") %>% 
    group_by(SIGN1, STFIPS, CTFIPS) %>%
    mutate(LENGTH = as.numeric(st_length(geometry))/meters.per.mile,
           Seg_Num = ceiling(cumsum(LENGTH) / segment.dist)) %>%
    group_by(SIGN1, STFIPS, CTFIPS, Seg_Num) %>% 
    summarise(geometry = st_union(st_combine(geometry)),
              AADT = mean(AADT), 
              LENGTH = as.numeric(st_length(geometry))/meters.per.mile) %>% 
    mutate(Seg_Num = ifelse((LENGTH < 10) & (Seg_Num > 1), Seg_Num - 1, Seg_Num)) %>%
    group_by(SIGN1, STFIPS, CTFIPS, Seg_Num) %>%
    summarise(geometry = st_union(st_combine(geometry)),
              AADT = mean(AADT), 
              LENGTH = as.numeric(st_length(geometry))/meters.per.mile)
  
  # Short roads and long/cut-up roads are appended into one dataset
  
  hwys.arr <- hwys.test %>%
      filter(LENGTH <= (segment.dist + short.road.exclusion)) %>%
     # select(-CTFIPS) %>%
      mutate(Seg_Num = 1) %>%
      rbind(., hwys.too.long) %>%
      group_by(SIGN1, STFIPS, CTFIPS, Seg_Num) %>%
      summarise(AADT = mean(AADT),
                geometry = st_union(st_combine(geometry))) %>%
      mutate(LENGTH =  as.numeric(st_length(geometry))/meters.per.mile, 
             Seg_ID = paste0(SIGN1, "_", STFIPS, "_", CTFIPS, "_", Seg_Num))

  # 1 mile buffer added 
  
  hwys.buff <- st_buffer(hwys.arr, dist = 1 * meters.per.mile, endCapStyle = "ROUND")

  # stations found within 1 mile of each road

  station.intersections <- st_intersection(hwys.buff, afdc.dcfc.proj)
  
  ### added to list of covered segments, new segments from state pre-processing
  if(all.chargers.flag){
    NEVI.seg <- station.intersections %>% filter(NEVI_count) %>% pull(Seg_ID) %>% unique() 
  }else{
    NEVI.seg <- station.intersections %>% filter(NEVI_count, !Tesla) %>% pull(Seg_ID) %>% unique() 
  }
  all.seg <- station.intersections %>% pull(Seg_ID) %>% unique()
  all.but.tesla.seg <- station.intersections %>% filter(!Tesla) %>% pull(Seg_ID) %>% unique()
  print('matched stations')
# This just makes one row per 50-mile segment, fewer data points to deal with...

  eligible.hwys <- hwys.arr %>% ungroup()%>% 
      group_by(Seg_ID) %>% # Method
      mutate(NEVI = Seg_ID %in% NEVI.seg,
             Has_EV = Seg_ID %in% all.seg,
             No_Tesla = Seg_ID %in% all.but.tesla.seg,
             Traffic = AADT, # * LENGTH,
             ) %>% ungroup() %>% group_by(Seg_ID) %>%
      summarise(geometry = st_union(st_combine(geometry)), # lots of binary labeling
                SIGN1 = first(SIGN1), # road name
                STFIPS = first(STFIPS), # state
                Seg_ID = first(Seg_ID), # identifier
                NEVI = max(NEVI), # if it meets NEVI requirements (4 DC fast chargers)
                Has_EV = max(Has_EV), # if it has any level 2 or DC chargers
                No_Tesla = max(No_Tesla), # all chargers but Tesla
                Traffic = mean(Traffic), # average traffic
                Short_Road = ifelse(LENGTH <= short.road.exclusion, TRUE, FALSE), # If the total road is <10 miles
                LENGTH =  as.numeric(st_length(geometry))/meters.per.mile,
                ) %>% ungroup()
  eligible.hwys$ID <- 1:nrow(eligible.hwys)
  print('segments')

# Finds which roads are AFC segments
  # matches by name (PRIMARY_NA & SIGN1) and by location within a quarter mile buffer of network
  # This doesn't include AFCs that are not in the national highway system because we don't have traffic
  # info for those AFCs anyways, which is how the roads get weighted in the metric
  
  afc <-  read_sf(paste0(folder.name, afc.net.file))
  afc <- st_transform(afc, crs = st_crs(proj.contig))
  state.letters<- read_csv(paste0(file.path, "state_fips.csv"), show_col_types = FALSE)
  afc <- merge(x=afc, y = state.letters, by.x = 'STATE', by.y = 'letters')
  
  afc <- afc %>% filter(EV != 0) %>% 
                 mutate(PRIMARY_NA = ifelse(is.na(PRIMARY_NA), 'WITHOUT_SIGN', PRIMARY_NA),
                        SIGN1 = PRIMARY_NA,
                        ROUTEID = PRIMARY_NA) %>%
                 select(SIGN1, ROUTEID, STFIPS) %>% 
                 group_by(SIGN1, STFIPS) %>%
                 summarise(geometry = st_union(st_combine(geometry))) %>%
                 ungroup() %>% mutate(AFC_ID = row_number())
  overlap.buffer <- st_buffer(eligible.hwys %>% filter(SIGN1 %in% afc$SIGN1), dist = (0.25 * meters.per.mile), endCapStyle = 'ROUND')
  overlap.buffer <- st_buffer(overlap.buffer, dist=0)
  overlapping <- st_intersection(st_make_valid(overlap.buffer), afc) %>% filter(SIGN1 == SIGN1.1)
  
  #finding any remaining ones
  afc.buff <-st_buffer(afc, dist = (0.5 * meters.per.mile), endCapStyle = 'ROUND')
  afc.check <- data.frame(st_contains(afc.buff, eligible.hwys))
  colnames(afc.check) <- c('AFC_ID', 'hwys_ID')
  eligible.hwys <- eligible.hwys %>% mutate(AFC = (Seg_ID %in% overlapping$Seg_ID) | (ID %in% afc.check$hwys_ID))
  
  remaining.afc <- afc %>% filter(!(AFC_ID %in% overlapping$AFC_ID) & !(AFC_ID %in% afc.check$AFC_ID))
  afc.stations <- st_intersection(afc.buff %>% filter(AFC_ID %in% remaining.afc$AFC_ID), afdc.dcfc.proj)
    
  # AFCs not in NHS are given mean traffic for state
  state.traffic <- eligible.hwys %>% st_drop_geometry() %>% 
    group_by(STFIPS) %>% summarise(Traffic = mean(Traffic))
  
  # made to match NHS data
  remaining.afc <- remaining.afc %>% merge(state.traffic, by = 'STFIPS') %>%
    mutate(Seg_ID = paste0(SIGN1, "_", STFIPS, "_",'AFC', "_", row_number()), # identifier
           NEVI = AFC_ID %in% (afc.stations %>% filter(NEVI_count, !Tesla) %>% pull(AFC_ID)),
           Has_EV = AFC_ID %in% (afc.stations %>% pull(AFC_ID)), 
           No_Tesla = AFC_ID %in% (afc.stations %>% filter(!Tesla) %>% pull(AFC_ID)), # average traffic
           LENGTH =  as.numeric(st_length(geometry))/meters.per.mile,
           Short_Road = ifelse(LENGTH <= short.road.exclusion, TRUE, FALSE), # If the total road is <10 miles
           ID = row_number() + length(eligible.hwys$ID),
           AFC = TRUE) %>% select(colnames(eligible.hwys))
  eligible.hwys <- rbind(eligible.hwys, remaining.afc)
  
  ####
  eligible.hwys.drop <- st_drop_geometry(eligible.hwys)
  
  print('matched AFCs')
  # Finds every road segment that touches every other one (within a 1/4 mile buffer)

  st_precision(eligible.hwys) <- 0.1
  eligible.buff <- st_buffer(eligible.hwys, dist = 0.25 * meters.per.mile)
  touching <- st_overlaps(st_make_valid(eligible.buff))
  touching.segments <- data.table(data.frame(touching))
  colnames(touching.segments) <- c('ID', 'ID_match')
  
  # This makes the touching segments a segment ID based dataframe instead of an array of arrays

  touching.segments <- merge(x = touching.segments, 
                             y = eligible.hwys.drop %>% select(ID, Seg_ID), 
                             by = "ID")
  touching.segments <- merge(x = touching.segments, 
                             y = eligible.hwys.drop %>% 
                               mutate(Seg_ID_match = Seg_ID) %>% 
                               select(ID, Seg_ID_match), 
                             by.x = "ID_match", by.y = "ID")

  print('touching segments found')
# create county population center 50-mile buffer

  county.pop.centers <- read_sf(paste0(file.path, county.pop.center.file)) %>%
                    st_as_sf(coords=c("LONGITUDE", "LATITUDE"), crs = st_crs(4326)) %>%
                    mutate(GEOID = gsub(' ', '0', paste0(formatC(STATEFP, digits=1), formatC(COUNTYFP, digits = 2)))) %>%
                    st_transform(crs=st_crs(proj.contig))
  
  county.buffers <- st_buffer(county.pop.centers, dist = (meters.per.mile * segment.dist))
  
  st_precision(county.buffers) <- 0.1
  st_precision(eligible.hwys) <- 0.1
  
  # If the range considered is not the whole country (500 miles or 100 miles etc)
  # Find the segments within the range that is set by range.dist
  if (!is.na(range.dist)){
    county.ranges <- st_buffer(county.pop.centers, dist = (meters.per.mile * range.dist))
  }
  # Finds which segments are in which county population center 50-mile buffer
  county.segments <- st_intersection(eligible.hwys, county.buffers) %>% 
                     st_drop_geometry() %>%
                     select(Seg_ID, ID, GEOID, STATEFP, COUNTYFP) %>% data.table()

# write all datasets to a folder (2023)

  write_csv(touching.segments, paste0(file.path, 'results/2023/touching_datatable.csv'))
  write.csv(eligible.hwys.drop, paste0(file.path, 'results/2023/eligible_hwys/eligible_hwys.csv'))
  write_sf(eligible.hwys, paste0(file.path, 'results/2023/eligible_hwys/eligible_hwys.shp'))
  write.csv(county.segments, paste0(file.path, 'results/2023/county_intersections.csv'))

}else{
  
  # If the above section has been run before, set `data.processing` to false and read in
  
  eligible.hwys <- read_sf(paste0(file.path, 'results/2023/eligible_hwys/eligible_hwys.shp')) %>%
                   st_transform(crs = st_crs(proj.contig))
  DACs <- read_sf(paste0(file.path, DAC.file)) %>% st_transform(crs = st_crs(proj.contig))
  counties <- read_sf(paste0(folder.name, county.file)) %>%
                   st_transform(crs = st_crs(proj.contig))
  county.pop.centers <- read_sf(paste0(file.path, county.pop.center.file)) %>%
                    st_as_sf(coords=c("LONGITUDE", "LATITUDE"), crs = st_crs(4326)) %>%
                    mutate(GEOID = gsub(' ', '0', paste0(formatC(STATEFP, digits=1), formatC(COUNTYFP, digits = 2)))) %>%
                    st_transform(crs=st_crs(proj.contig))
  
  county.buffers <- st_buffer(county.pop.centers, dist = (meters.per.mile * segment.dist))
  if (!is.na(range.dist)){
    county.ranges <- st_buffer(county.pop.centers, dist = (meters.per.mile * range.dist))
  }
  county.segments <- read_csv(paste0(file.path, 'results/2023/county_intersections.csv'), show_col_types = FALSE)
  touching.segments <- read_csv(paste0(file.path, 'results/2023/touching_datatable.csv'), show_col_types = FALSE)
  eligible.hwys.drop <- read_csv(paste0(file.path, 'results/2023/eligible_hwys/eligible_hwys.csv'), show_col_types = FALSE)
  st_precision(county.buffers) <- 0.1
  st_precision(eligible.hwys) <- 0.1
}
beep()
```


# Calculates coverage metric for each county


```{r}
full.county.coverage <- data.frame()
counties <- unique(county.segments$GEOID)
st_agr(eligible.hwys) = "constant"
i <- 0
for (county.ID in counties){
  state.fips <- as.numeric(substr(county.ID, 1, 2))
  i <- i + 1
  if (i%%500 ==0){
    print(i)
  }
  # the roots of the search function are all of the segments in the county
  roots <- county.segments[county.segments$GEOID == county.ID, ]$Seg_ID
  
  # full.range is the set of all segments in range of the county
  if (!is.na(range.dist)){
    county.range <- county.ranges[county.ranges$GEOID == county.ID, ]
    st_agr(county.range) = "constant"
    county.range.segments <- st_intersection(eligible.hwys, county.range) %>% 
                       st_drop_geometry() %>%
                       select(Seg_ID, ID, GEOID, STATEFP, COUNTYFP) %>% data.table()
    full.range <- county.range.segments[county.range.segments$GEOID == county.ID, ]$Seg_ID
  }else{
    full.range <- eligible.hwys$Seg_ID
  }
  
  # marks any county in county as 'In_County' grabs only segments in-range
  eligible.hwys.county <- eligible.hwys.drop %>% filter(Seg_ID %in% full.range) %>% mutate(In_County = Seg_ID %in% roots)
  
  # any road segment in the county that touches another segment can be the starting point
  # for the breadth-first-search
  seed.IDs <- eligible.hwys.county %>% 
    filter(In_County, !Short_Road, (Seg_ID %in% touching.segments$Seg_ID)) %>% 
    pull(Seg_ID)
  
  # If there are no highways that leave a county (some very rural middle-america counties)
  # just consider segments in the county (rare)
  if (length(seed.IDs)==0){
    numerator.afc <- eligible.hwys.county %>% filter((In_County), !Short_Road) %>% 
      mutate(weight = Traffic) %>% pull(weight) %>% sum()
    numerator.all <- eligible.hwys.county %>% filter((In_County), !Short_Road) %>% 
      mutate(weight = Traffic) %>% pull(weight) %>% sum()
    numerator <- eligible.hwys.county %>% filter((In_County), !Short_Road) %>% 
      mutate(weight = Traffic) %>% pull(weight) %>% sum()
    numerator.spill <- 0
  }else{
    # for AFC scenario, grab all eligible segments and make a iGraph graph
    eligible.segments.afc.ID <- filter(eligible.hwys.county, (NEVI | Short_Road | AFC | In_County)) %>% pull(Seg_ID)
    graph.tree.afc <- graph.data.frame(touching.segments[,c('Seg_ID','Seg_ID_match')] %>% filter(Seg_ID %in% eligible.segments.afc.ID))
    # this is the breadth first search function that starts with every seed segment in county
    cluster.tree.afc <- subcomponent(graph.tree.afc, seed.IDs, mode = "out")
    # finds accessible segments
    cluster.afc.IDs <- cluster.tree.afc$name
    # calculates numerator as the traffic of all of the accessible segments
    numerator.afc <- eligible.hwys.drop %>% 
      filter((Seg_ID %in% cluster.afc.IDs), !Short_Road, (Seg_ID %in% full.range)) %>% 
      mutate(weight = Traffic) %>% pull(weight) %>% sum()
    
    # if true, include TESLA stations, otherwise do not
    if(all.chargers.flag){
      eligible.segments.all.ID <- filter(eligible.hwys.county, (Has_EV | Short_Road | In_County)) %>% pull(Seg_ID)
    }else{
      eligible.segments.all.ID <-  filter(eligible.hwys.county, (No_Tesla | Short_Road | In_County)) %>% pull(Seg_ID)
    }
    # this makes a graph/network of the segments, from the list of what segments each touches
    # same process as above but excluding AFCs that do not already have a station
    graph.tree.all <- graph.data.frame(touching.segments[,c('Seg_ID','Seg_ID_match')] %>% filter(Seg_ID %in% eligible.segments.all.ID))
    cluster.tree.all <- subcomponent(graph.tree.all, seed.IDs, mode = "out")
    cluster.all.IDs <- cluster.tree.all$name
    numerator.all <- eligible.hwys.drop %>% 
      filter((Seg_ID %in% cluster.all.IDs), !Short_Road,(Seg_ID %in% full.range)) %>% 
      mutate(weight = Traffic) %>% pull(weight) %>% sum()
    numerator.spill <- eligible.hwys.drop %>% 
      filter((Seg_ID %in% cluster.all.IDs), !(STFIPS == state.fips), !Short_Road, (Seg_ID %in% full.range)) %>% 
      mutate(weight = Traffic) %>% pull(weight) %>% sum()
    
  # same process as above but excluding AFCs that do not already have a station
  eligible.segments.ID <- filter(eligible.hwys.county, (NEVI | Short_Road | In_County)) %>%  pull(Seg_ID)
  graph.tree <- graph.data.frame(touching.segments[,c('Seg_ID','Seg_ID_match')] %>% filter(Seg_ID %in% eligible.segments.ID))
    cluster.tree <- subcomponent(graph.tree, seed.IDs, mode = "out")
    cluster.IDs <- cluster.tree$name
    numerator <- eligible.hwys.drop %>% 
      filter((Seg_ID %in% cluster.IDs), !Short_Road,(Seg_ID %in% full.range)) %>% 
      mutate(weight = Traffic) %>% pull(weight) %>% sum()
  }
  # all coverage scenarios have the same baseline (all roads in range of starting buffer)
  denominator <- eligible.hwys.drop %>% filter(!Short_Road, (Seg_ID %in% full.range)) %>% 
    mutate(weight = Traffic) %>% pull(weight) %>% sum()
  county.coverage <- data.frame('county' = county.ID, 
                                'Baseline coverage' = (numerator.all/denominator), 
                                'Spillover State coverage' = (numerator.spill/denominator),
                                'NEVI coverage' = (numerator/denominator),
                                'AFC coverage' = (numerator.afc/denominator))
  # append to full set
  full.county.coverage <- rbind(full.county.coverage, county.coverage)
}
full.county.coverage <- full.county.coverage %>% mutate(`NEVI Increase` = `AFC.coverage`-`NEVI.coverage`)
# rename column depending on if Tesla was included
#colnames(full.county.coverage)[2] <- ifelse(all.chargers.flag, 'Baseline coverage', 'All but Tesla coverage')
beep()
```

```{r}
if(all.chargers.flag){
  write_csv(full.county.coverage, paste0(file.path, 'results/2023/', paste0('county_coverage_with_tesla.csv')))
}else{
  write_csv(full.county.coverage, paste0(file.path, 'results/2023/', paste0('county_coverage_no_tesla.csv')))
}

```

```{r}
#full.county.coverage <- read_csv(paste0(file.path, 'results/2023/', paste0('county_coverage_no_tesla.csv')))
```

```{r}
fast_chargers_needed <- eligible.hwys %>% filter(!(STFIPS %in% c(2, 60, 66, 69, 72, 78, 15)), !NEVI, !Short_Road) %>% pull(Seg_ID) %>% length() # 6316 + 55 AK + 16 HI, 5260 with Tesla + 51 with AK +16 HI
print(fast_chargers_needed)
fast_chargers_needed_afc <- eligible.hwys %>% filter(!(STFIPS %in% c(2, 60, 66, 69, 72, 78, 15)), !NEVI, !Short_Road, !AFC) %>% pull(Seg_ID) %>% length() 
fast_chargers_needed_afc # 4408 +43 AK + 0 HI, 3914 with Tesla + 40 AK + 0 HI if tesla is accessible
# 1908 needed on AFCs
# 1346 needed on AFCs if Tesla chargers are accessible
```


