## Process Baseline Corridor Charging Availability 
# Author: Catherine Ledna & Lily Hanig
# Date: 08/05/2022

#
### National Highway system
# https://www.fhwa.dot.gov/planning/national_highway_system/nhs_maps/

### Alternative Fuel Corridors 
# https://hepgis.fhwa.dot.gov/fhwagis/ViewMap.aspx?map=Highway+Information|Electric+Vehicle+(EV-Round+1,2,3,4,5+and+6)#

### EV stations
# https://afdc.energy.gov/stations/#/analyze?fuel=ELEC&status=E&status=P

### disadvantaged communities shapefile DOT
# https://www.transportation.gov/equity-Justice40

# Population centers 
# https://www2.census.gov/geo/docs/reference/cenpop2020/county/CenPop2020_Mean_CO.txt

```{r}
library(sf)
library(rgdal)
library(data.table)
library(dplyr)
library(igraph)
library(here)
library(beepr)
library(tidyverse)
library(lwgeom)


segment.dist <- 50 # miles
range.dist <- 500 # miles
short.road.exclusion <- 10 # miles
meters.per.mile <- 1609.34
options(dplyr.summarise.inform = FALSE)

```

```{r}

  proj.contig <- 5070 # 4326 # 
  proj.isl <- 5070
  proj.ak <- 3338
  
  
  net.file <- "nhs20221230/NHS_20221230.shp"                        #"nhs20210815/National_NHS_2021-08-23.shp"
  afc.net.file <- "AltFuels_Rounds1-6_2022-07-26/AltFuels_Rounds1-6_2022-07-26.shp"
  alt.fuel.stations <- "alt_fuel_stations_3_1_2023.csv"  
  alt.fuel.stations.trucks <- "alt_fuel_stations_04_09_2024.csv"
  #"alt_fuel_stations_10_17_2022.csv"
  DAC.file <- "shapefiles/DOT_DAC/DOT_Disadvantage_Layer_Final_April2022.shp"
  net.folder <- "nhs2019"
  county.file <- "tl_2020_us_county/tl_2020_us_county.shp"
  county.file.ak <- "tl_2018_02_cousub/tl_2018_02_cousub.shp"
  county.pop.center.file <- "CenPop2020_Mean_CO.csv"
  county.center.file <- "2020_us_population_center_county.csv"
  #Documents/Research/EV_NREL
  file.path <- here("data/")       #../corridor_coverage_project                                  #here("Research/EV_NREL/data/")
  folder.name <- here("../corridor_coverage_project/data/shapefiles/")
  state.file <- "tl_2022_us_state/tl_2022_us_state.shp"
  cb.state.file <- "cb_2018_us_state/cb_2018_us_state_20m.shp"

```

```{r}
counties <- read_sf(paste0(folder.name, county.file)) %>%
  st_transform(crs = st_crs(proj.contig))
                 
```
# Read in files
```{r}

eligible.hwys <- read_sf(paste0(file.path, 'results/2023/eligible_hwys/eligible_hwys_500.shp')) %>%
                 st_transform(crs = st_crs(proj.contig))
DACs <- read_sf(paste0(file.path, DAC.file)) %>% st_transform(crs = st_crs(proj.contig))
counties <- read_sf(paste0(folder.name,county.file.ak)) %>%
                   st_transform(crs = st_crs(proj.contig)) %>%  
  mutate(GEOID = substr(GEOID, 1, 5))
counties<- merge(x=counties, y=full.county.coverage, by.x = 'GEOID', by.y = 'county', all=T)
vehicles.per.county <- read_csv(paste0(file.path, 'vehicles_per_county.csv'))
counties <- merge(x=counties, y= vehicles.per.county, by = 'GEOID',all=T) #
county.pop.centers <- read_sf(paste0(file.path, county.pop.center.file)) %>%
                  st_as_sf(coords=c("LONGITUDE", "LATITUDE"), crs = st_crs(4326)) %>%
                  mutate(GEOID = gsub(' ', '0', paste0(formatC(STATEFP, digits=1), formatC(COUNTYFP, digits = 2)))) %>%
                  st_transform(crs=st_crs(proj.contig))

county.buffers <- st_buffer(county.pop.centers, dist = (meters.per.mile * segment.dist))
if (!is.na(range.dist)){
  county.ranges <- st_buffer(county.pop.centers, dist = (meters.per.mile * range.dist))
}
county.segments <- read_csv(paste0(file.path, 'results/2023/county_intersections_500.csv'), show_col_types = FALSE)
touching.segments <- read_csv(paste0(file.path, 'results/2023/touching_datatable_500.csv'), show_col_types = FALSE)
eligible.hwys.drop <- read_csv(paste0(file.path, 'results/2023/eligible_hwys/eligible_hwys_500.csv'), show_col_types = FALSE)
st_precision(county.buffers) <- 0.1
st_precision(eligible.hwys) <- 0.1

#beep(sound=3)
```


# Read in coverage per county

# Read in county shapefile and state shapefile, match the coverage to each
# weight state-level coverage by number of registered vehicles
```{r}
all.chargers.flag <- FALSE
read.in <-TRUE
ending <- '500'
if (read.in){
  if(all.chargers.flag){
    full.county.coverage <- read_csv(paste0(file.path, 'results/2023/', paste0('county_coverage_with_tesla_', ending, '.csv')))
  }else{
    full.county.coverage <- read_csv(paste0(file.path, 'results/2023/', paste0('county_coverage_no_tesla_', ending, '.csv')))
  }
}



counties <- read_sf(paste0(folder.name, county.file)) %>%
                   st_transform(crs = st_crs(proj.contig))%>%  
  mutate(GEOID = substr(GEOID, 1, 5))
counties<- merge(x=counties, y=full.county.coverage, by.x = 'GEOID', by.y = 'county', all=T)
vehicles.per.county <- read_csv(paste0(file.path, 'vehicles_per_county.csv'))
counties <- merge(x=counties, y= vehicles.per.county, by = 'GEOID', all=T) %>% replace(is.na(.), 0)

state.coverage <- counties %>% st_drop_geometry() %>% group_by(STATEFP) %>%
                     summarise(`Baseline Coverage` = weighted.mean(`Baseline.coverage`, Vehicles),
                               `NEVI Coverage` = weighted.mean(`NEVI.coverage`, Vehicles),
                               `AFC Coverage` = weighted.mean(`AFC.coverage`, Vehicles),
                               `State Spillover` = weighted.mean(`Spillover.State.coverage`, Vehicles),
                               `NEVI Increase` = weighted.mean(`NEVI Increase`, Vehicles))

states <- read_sf(paste0(folder.name, cb.state.file)) %>%
                   st_transform(crs = st_crs(proj.contig)) %>%
              merge(state.coverage, by.x = "GEOID", by.y = 'STATEFP')

state.letters<- read_csv(paste0(file.path, "state_fips.csv"), show_col_types = FALSE)

commuters <- read_csv(paste0(file.path, 'commute_data.csv'), show_col_types = FALSE)

#write.csv(st_drop_geometry(states), paste0(file.path, 'results/2023/', 'state_coverage_contiguous_', ending,'.csv'))
```

### plot the coverage at the state level (weighted by vehicle registration per county) for baseline
```{r}

ggplot()+geom_sf(data=states %>% filter((STATEFP %in% c('15'))), aes(fill=`Baseline Coverage`), colour = alpha("gray70", 1 / 2), size = 0.2)+ scale_fill_gradientn(colors=c("#fbfddf", "#e1e96b","#8da72a","#4E8E5B", "#0e758c"),limits = c(0,1))+
  guides(fill = guide_colourbar(title = "Minimum Viable\nCoverage\n(tesla)"))+theme_minimal() +theme(panel.grid = element_blank())
```

# plot the coverage at the state level (weighted by vehicle registration per county) for NEVI-compliant only
```{r}

ggplot()+geom_sf(data=states %>% filter((STATEFP %in% c('15'))), aes(fill=`NEVI Coverage`), colour = alpha("gray70", 1 / 2), size = 0.2)+ scale_fill_gradientn(colors=c("#fbfddf", "#e1e96b","#8da72a","#4E8E5B", "#0e758c"),limits = c(0,1))+ theme_minimal()+ guides(fill = guide_colourbar(title = "Fast Charger\nCoverage\n")) +theme(panel.grid = element_blank())
```

# plot the coverage at the state level (weighted by vehicle registration per county) for NEVI-compliant and AFC only
```{r}
# , '72', '60', '69', '78', '66', '15'
ggplot()+geom_sf(data=states %>% filter((STATEFP %in% c('02'))), aes(fill=`AFC Coverage`), colour = alpha("gray70", 1 / 2), size = 0.2)+ scale_fill_gradientn(colors=c("#fbfddf", "#e1e96b","#8da72a","#4E8E5B", "#0e758c"),limits = c(0,1))+ theme_minimal()+ guides(fill = guide_colourbar(title = "AFCs Reach\nNEVI-compliant\nStatus")) +theme(panel.grid = element_blank())
```

# County level
#plot the coverage at the county level for baseline coverage
```{r}
#, '02', '72', '60', '69', '78', '66','15'
ggplot()+geom_sf(data=counties %>% filter((STATEFP %in% c('15'))) %>% mutate(Baseline.coverage = replace_na(Baseline.coverage, 0)), aes(fill=0), colour = alpha("gray70", 1 / 2), size = 0.2)+ scale_fill_gradientn(colors=c("#fbfddf", "#e1e96b","#8da72a","#4E8E5B", "#0e758c"),limits = c(0,1))+ theme_minimal()+
  guides(fill = guide_colourbar(title = "minimum viable coverage\nlevel 2 & DC chargers\n(600 miles)")) +theme(panel.grid = element_blank())
```

#plot the coverage at the county level for NEVI-compliant stations and AFCs
# %>% mutate(AFC.coverage = replace_na(AFC.coverage, 0))
```{r}
ggplot()+geom_sf(data=counties %>% filter(!(STATEFP %in% c('02', '15', '72', '60', '69', '78', '66')))%>% mutate(AFC.coverage = replace_na(AFC.coverage, 0)), aes(fill=`AFC.coverage`), colour = alpha("gray70", 1 / 2), size = 0.2)+ scale_fill_gradientn(colors=c("#fbfddf", "#e1e96b","#8da72a","#4E8E5B", "#0e758c"),limits = c(0,1))+ 
 # geom_sf(data=eligible.hwys%>% filter((AFC==1), !(STFIPS %in% c(2, 15, 72, 60, 69, 78, 66))), color = '#d9d2e9')+
  theme_minimal()+ guides(fill = guide_colourbar(title = "AFCs reach\nNEVI-compliance\n(600 miles)"))# +theme(panel.grid = element_blank())
```

#plot the coverage at the county level for NEVI-compliant stations only
```{r}
# , '02', 
ggplot()+geom_sf(data=counties %>% filter(!(STATEFP %in% c('02', '15', '72', '60', '69', '78', '66')))
                 %>% mutate(NEVI.coverage = replace_na(NEVI.coverage, 0)),
                 aes(fill=`NEVI.coverage`), colour = alpha("gray70", 1 / 2), size = 0.2)+ scale_fill_gradientn(colors=c("#fbfddf", "#e1e96b","#8da72a","#4E8E5B", "#0e758c"),limits = c(0,1))+ theme_minimal()+ guides(fill = guide_colourbar(title = "minimum 4\nDC fast chargers\n(600 miles)"))#+theme(panel.grid = element_blank())
```
```{r}

states <- read.csv(paste0(file.path, 'results/2023/', 'state_coverage_contiguous_', ending,'.csv'))
```
# Pick a specific county to run
# the regions are the states that should be included in a map for a certain state,
# (17=Illinois and should include Indiana, Iowa, etc.)

```{r}

county.ID <- "36061" ##"48201"#"17031"#"08031"# "36061"# "06075" 

state.fips <- as.numeric(substr(county.ID, 1, 2))
regions <- vector(mode='list', length=55)
regions[[17]] <- c('17', '18', '19', '55', '29', '21', '39', '26', '21', '27', '54', '47') # IL
regions[[36]] <- c('36', '09', '42', '34', '25', '50', '33', '44', '23', '51', '54', '39', '24', '44', '37', '26') # NY
regions[[6]] <- c('06', '32', '41', '04', '49') # CA
regions[[8]] <- c('08', '04', '49', '35', '56', '31', '20', '46', '40', '16', '30') # 48
regions[[48]] <- c('48', '22', '05', '40', '28')
```

# Get the segments that are covered for a specific county
```{r}
st_agr(eligible.hwys) = "constant"

# the roots of the search function are all of the segments in the county
roots <- county.segments[county.segments$GEOID == county.ID, ]$Seg_ID
if (!is.na(range.dist)){
  county.range <- county.ranges[county.ranges$GEOID == county.ID, ]
  st_agr(county.range) = "constant"
  county.range.segments <- st_intersection(eligible.hwys, county.range) %>% 
                     st_drop_geometry() %>%
                     select(Seg_ID, ID, GEOID, STATEFP, COUNTYFP) %>% data.table()
  full.range <- county.range.segments[county.range.segments$GEOID == county.ID, ]$Seg_ID
}else{
  full.range <- eligible.hwys$Seg_ID
}

# marks any county in county as 'In_County'
eligible.hwys.county <- eligible.hwys.drop %>% filter(Seg_ID %in% full.range) %>% mutate(In_County = Seg_ID %in% roots)

seed.IDs <- eligible.hwys.county %>% 
  filter(In_County, !Short_Road, (Seg_ID %in% touching.segments$Seg_ID)) %>% 
  pull(Seg_ID)

if (length(seed.IDs)==0){
  numerator.afc <- eligible.hwys.county %>% filter((In_County), !Short_Road) %>% 
    mutate(weight = Traffic) %>% pull(weight) %>% sum()
  numerator.all <- eligible.hwys.county %>% filter((In_County), !Short_Road) %>% 
    mutate(weight = Traffic) %>% pull(weight) %>% sum()
  numerator <- eligible.hwys.county %>% filter((In_County), !Short_Road) %>% 
    mutate(weight = Traffic) %>% pull(weight) %>% sum()
}else{
  eligible.segments.afc.ID <- filter(eligible.hwys.county, (NEVI | Short_Road | AFC | In_County)) %>% pull(Seg_ID)
  graph.tree.afc <- graph.data.frame(touching.segments[,c('Seg_ID','Seg_ID_match')] %>% filter(Seg_ID %in% eligible.segments.afc.ID))
  cluster.tree.afc <- subcomponent(graph.tree.afc, seed.IDs, mode = "out")
  cluster.afc.IDs <- cluster.tree.afc$name
  numerator.afc <- eligible.hwys.drop %>% 
    filter((Seg_ID %in% cluster.afc.IDs), !Short_Road, (Seg_ID %in% full.range)) %>% 
    mutate(weight = Traffic) %>% pull(weight) %>% sum()
  
  if(all.chargers.flag){
    eligible.segments.all.ID <- filter(eligible.hwys.county, (Has_EV | Short_Road | In_County)) %>% pull(Seg_ID)
  }else{
    eligible.segments.all.ID <-  filter(eligible.hwys.county, (No_Tesla | Short_Road | In_County)) %>% pull(Seg_ID)
  }
  # this makes a graph/network of the segments, from the list of what segments each touches
  graph.tree.all <- graph.data.frame(touching.segments[,c('Seg_ID','Seg_ID_match')] %>% filter(Seg_ID %in% eligible.segments.all.ID))
  cluster.tree.all <- subcomponent(graph.tree.all, seed.IDs, mode = "out")
  cluster.all.IDs <- cluster.tree.all$name
  numerator.all <- eligible.hwys.drop %>% 
    filter((Seg_ID %in% cluster.all.IDs), !Short_Road,(Seg_ID %in% full.range)) %>% 
    mutate(weight = Traffic) %>% pull(weight) %>% sum()
  
eligible.segments.ID <- filter(eligible.hwys.county, (NEVI | Short_Road | In_County)) %>%  pull(Seg_ID)
graph.tree <- graph.data.frame(touching.segments[,c('Seg_ID','Seg_ID_match')] %>% filter(Seg_ID %in% eligible.segments.ID))
  cluster.tree <- subcomponent(graph.tree, seed.IDs, mode = "out")
  cluster.IDs <- cluster.tree$name
  numerator <- eligible.hwys.drop %>% 
    filter((Seg_ID %in% cluster.IDs), !Short_Road,(Seg_ID %in% full.range)) %>% 
    mutate(weight = Traffic) %>% pull(weight) %>% sum()
}
denominator <- eligible.hwys.drop %>% filter(!Short_Road, (Seg_ID %in% full.range)) %>% 
  mutate(weight = Traffic) %>% pull(weight) %>% sum()
county.coverage <- data.frame('county' = county.ID, 
                              'Baseline coverage' = (numerator.all/denominator), 
                              'NEVI coverage' = (numerator/denominator),
                              'AFC coverage' = (numerator.afc/denominator))

colnames(county.coverage)[2] <- ifelse(all.chargers.flag, 'Baseline coverage', 'All but Tesla coverage')

```

# Plot the covered segments in the baseline case including all chargers

```{r}
# all chargers
g1 <- ggplot()+geom_sf(data= states %>% filter(STATEFP %in% regions[[state.fips]]), fill = '#f7f9ff')+
  geom_sf(data=eligible.hwys%>% filter(Seg_ID %in% full.range),aes(color='roads'))+
  geom_sf(data=eligible.hwys%>% filter((Seg_ID %in% full.range), (Has_EV==1)),aes(color='chargers'))+
  geom_sf(data=eligible.hwys%>% filter(Seg_ID %in% cluster.all.IDs), aes(color='access'))+theme_bw()+
  scale_color_manual('Charging Station Access\n(500 mile radius)', 
                     values = c('roads' = '#b4c2da', 'chargers' = '#f2a649', 'access' = '#00337c'), labels = c('Contiguous coverage', 'all charging stations', 'All highways'))+ ggtitle('2023 Coverage\n(level 2 & DC chargers)') + theme(plot.title = element_text(size = 10, hjust = 0.05, vjust = 1), legend.position = 'none')
g1
```

# Plot the covered segments in the baseline case including only NEVI-compliant chargers
```{r}
# nevi compliant
g2<- ggplot()+geom_sf(data= states%>% filter(STATEFP %in% regions[[state.fips]]), fill = '#f7f9ff')+
  geom_sf(data=eligible.hwys%>% filter(Seg_ID %in% full.range), aes(color = 'roads'))+
  geom_sf(data=eligible.hwys%>% filter(Seg_ID %in% full.range, NEVI==1), aes(color = 'afcchargers'))+
  geom_sf(data=eligible.hwys%>% filter(Seg_ID %in% cluster.IDs),  aes(color = 'access'))+theme_bw()#+
  scale_color_manual('NEVI-compliant stations\n(500 mile radius)', 
                     values = c('roads' = '#b4c2da', 'afcchargers' = '#ff6363', 'access'='#00337c'),
                     labels = c('Contiguous coverage','NEVI-compliant stations', 'All highways'))+ labs(tag = "NEVI-compliant only")
```

# Plot the covered segments in the baseline case including only NEVI-compliant chargers and AFCs
```{r}
# AFCs built
g3 <- ggplot()+geom_sf(data= states%>% filter(STATEFP %in% regions[[state.fips]]), fill = '#f7f9ff')+
  geom_sf(data=eligible.hwys%>% filter(Seg_ID %in% full.range), aes(color = 'roads'))+
  geom_sf(data=eligible.hwys%>% filter(Seg_ID %in% full.range, (NEVI==1 | AFC==1)), aes(color = 'afcchargers'))+
  geom_sf(data=eligible.hwys%>% filter(Seg_ID %in% cluster.afc.IDs), aes(color='access'))+
  theme_bw()+scale_color_manual('Charging Station Access\n(500 mile radius)', 
                     values = c('roads' = '#b4c2da', 'afcchargers' = '#ff6363', 'access'='#00337c', 'chargers' = '#f2a649'),
                     labels =c('Contiguous coverage','NEVI-compliant stations','All highways', 'Any charging station'))+ ggtitle('2030 Coverage with AFCs complete\n(min. 4 DC fast chargers)') + theme(plot.title = element_text(size = 10, hjust = 0.05, vjust = 1), legend.position = 'none')
#g3
```

```{r}
g1+g3 + plot_layout(guides = "collect")

```


# State level
%>% filter(!(STATEFP %in% c('02', '60', '66', '69', '72', '78', '15')

### plot the coverage at the state level (weighted by vehicle registration per county) for baseline
```{r}

ggplot()+geom_sf(data=states %>% filter(STUSPS %in% c('AL')), aes(fill=`Baseline Coverage`), colour = alpha("gray70", 1 / 2), size = 0.2)+ scale_fill_gradientn(colors=c("#fbfddf", "#e1e96b","#8da72a","#4E8E5B", "#0e758c"),limits = c(0,1))+
  guides(fill = guide_colourbar(title = "Minimum Viable\nCoverage\n(1000 miles)"))+theme_minimal() +theme(panel.grid = element_blank())
```

# plot the coverage at the state level (weighted by vehicle registration per county) for NEVI-compliant only
```{r}

ggplot()+geom_sf(data=states %>% filter(STATEFP %in% c('02')), aes(fill=`NEVI Coverage`), colour = alpha("gray70", 1 / 2), size = 0.2)+ scale_fill_gradientn(colors=c("#fbfddf", "#e1e96b","#8da72a","#4E8E5B", "#0e758c"),limits = c(0,1))+ theme_minimal()+ guides(fill = guide_colourbar(title = "Fast Charger\nCoverage\n(1000 miles)")) +theme(panel.grid = element_blank())
```

# plot the coverage at the state level (weighted by vehicle registration per county) for NEVI-compliant and AFC only
```{r}

ggplot()+geom_sf(data=states %>% filter(STATEFP %in% c('02')), aes(fill=`AFC Coverage`), colour = alpha("gray70", 1 / 2), size = 0.2)+ scale_fill_gradientn(colors=c("#fbfddf", "#e1e96b","#8da72a","#4E8E5B", "#0e758c"),limits = c(0,1))+ theme_minimal()+ guides(fill = guide_colourbar(title = "AFCs Reach\nNEVI-compliant\nStatus (1000 miles)")) +theme(panel.grid = element_blank())
```

# County level
#plot the coverage at the county level for baseline coverage
```{r}

ggplot()+geom_sf(data=counties %>% filter(!STATEFP %in% c('02', '15', '72')) %>% mutate(Baseline.coverage = replace_na(Baseline.coverage, 0)), aes(fill=`Baseline.coverage`), colour = alpha("gray70", 1 / 2), size = 0.2)+ scale_fill_gradientn(colors=c("#fbfddf", "#e1e96b","#8da72a","#4E8E5B", "#0e758c"),limits = c(0,1))+ theme_minimal()+
  guides(fill = guide_colourbar(title = "minimum viable coverage\nlevel 2 & DC chargers\n(Heavy Duty Trucks)")) +theme(panel.grid = element_blank())
```

#plot the coverage at the county level for NEVI-compliant stations and AFCs

```{r}
ggplot()+geom_sf(data=counties %>% filter(STATEFP %in% c('02')) %>% mutate(AFC.coverage = replace_na(AFC.coverage, 0)), aes(fill=`AFC.coverage`), colour = alpha("gray70", 1 / 2), size = 0.2)+ scale_fill_gradientn(colors=c("#fbfddf", "#e1e96b","#8da72a","#4E8E5B", "#0e758c"),limits = c(0,1))+ 
  geom_sf(data=eligible.hwys%>% filter((AFC==1), (STFIPS %in% c(2))), color = '#d9d2e9')+
  theme_minimal()+ guides(fill = guide_colourbar(title = "AFCs reach\nNEVI-compliance\n(400 miles)")) +theme(panel.grid = element_blank())
```

#plot the coverage at the county level for NEVI-compliant stations only
```{r}
ggplot()+geom_sf(data=counties %>% filter(STATEFP %in% c('02'))
                 %>% mutate(NEVI.coverage = replace_na(NEVI.coverage, 0)),
                 aes(fill=`NEVI.coverage`), colour = alpha("gray70", 1 / 2), size = 0.2)+ scale_fill_gradientn(colors=c("#fbfddf", "#e1e96b","#8da72a","#4E8E5B", "#0e758c"),limits = c(0,1))+ theme_minimal()+ guides(fill = guide_colourbar(title = "minimum 4\nDC fast chargers\n(HD truck)"))+theme(panel.grid = element_blank())
```

# Plot all AFC roads
```{r}

ggplot()+geom_sf(data=states %>% filter(!(STATEFP %in% c('02', '60', '66', '69', '72', '78', '15'))), fill = '#f7f9ff')+ 
  geom_sf(data=eligible.hwys%>% filter(!(STFIPS %in% c(2, 60, 66, 69, 72, 78, 15))), aes(color=factor(AFC)))+scale_color_manual(" ", labels = c('National Highway System', 'Alternative Fuel Corridors'), values = c("#7fdbff", "#005249"))+theme_minimal()#+theme(legend.position = c(0.25,0.13))

```

```{r}
afdc.dcfc <- fread(paste0(file.path, alt.fuel.stations.trucks)) %>%
               select(`Fuel Type Code`, `State`, `ZIP`,`Status Code`, `Expected Date`, `EV DC Fast Count`,
                      `Geocode Status`, `Latitude`, `Longitude`, `ID`, `Open Date`, `Country`, `EV Connector Types`,`Maximum Vehicle Class`)%>%
              # filter(!(is.na(`EV DC Fast Count`)),`EV DC Fast Count` > 0) %>%
             #  filter(`Maximum Vehicle Class` == 'HD') %>%
               mutate(`Open_Date`=as.character(`Open Date`),
                      `Lat` = `Latitude`,
                      `long` = `Longitude`,
                      `EV DC Fast Count` = ifelse(is.na(`EV DC Fast Count`), 0, `EV DC Fast Count`),
                      `Open_Year` = as.numeric(strsplit(`Open_Date`, split = "/", fixed = T)[[1]][1]),
                      `Open_Year` = ifelse(is.na(`Open_Year`), 2022, Open_Year),
                      `Tesla` = grepl('TESLA', `EV Connector Types`),
                      `NEVI_count` = ifelse(`EV DC Fast Count` >= 4, TRUE, FALSE))
  
  
  afdc.dcfc <- st_as_sf(afdc.dcfc, coords=c("Longitude", "Latitude"), crs=st_crs(4326))
  afdc.dcfc.proj <- st_transform(afdc.dcfc, crs=st_crs(proj.contig))
```
  

# Plot charging stations
```{r}

#afdc.dcfc.proj <- merge(afdc.dcfc.proj, state.letters, by.x = 'State', by.y = 'letters')
ggplot()+geom_sf(data=states %>% filter((STATEFP %in% c('02'))), fill = '#f7f9ff')+ 
 # geom_sf(data=st_union(eligible.hwys%>% filter(!(STFIPS %in% c(2, 60, 66, 69, 72, 78, 15)))), color="#ddeeff")+
  geom_sf(data=afdc.dcfc.proj%>% filter((STFIPS %in% c(2)), !(ID==237731)), aes(color=`Maximum Vehicle Class`), alpha=1,size= 5)+
  scale_color_manual(" ", #values = c("FALSE"= "#e76f51","TRUE"="#16537e"), 
                     values = c("HD"= "darkorange","MD"="darkolivegreen"), 
                     labels = c('Medium & Heavy-Duty', 'Medium-Duty'))+
  theme_minimal()+theme(legend.position = 'none', panel.grid = element_blank())+ #c(0.63,0.13)
 guides(color = guide_legend(override.aes = list(size = 3))) #
```
```{r}
median_income <- read_csv(paste0(file.path, 'median_income.csv'), show_col_types = FALSE)
commuters <- merge(commuters, counties, by = c('GEOID')) %>% merge(median_income, by = c('GEOID'))
```

```{r}
#commuters <- commuters %>% filter(!(STATEFP %in% c('72'))) %>%select(car_truck_van, Median_household_income, time_to_work, `Baseline.coverage`, `NEVI.coverage`, `AFC.coverage`) %>% mutate(time_to_work = round(as.numeric(time_to_work)))
national_income_median <- 74755/1000
mean_county <-62326/1000
car_median <- median(commuters$car_truck_van)

p1 <- ggplot(commuters) + geom_point(aes(y = Median_household_income, x = `Baseline.coverage`, color = car_truck_van),alpha = 0.4)+theme_bw()+geom_hline(yintercept = car_median)+ylab('percent car commuter')+xlab('Minimum Viable Coverage')+scale_x_continuous(labels = scales::percent)+scale_y_continuous(labels = scales::dollar_format())+scale_color_viridis_c(option = "plasma", labels = scales::percent)

p2 <- ggplot(commuters) + geom_point(aes(y = Median_household_income/1000, x = `Baseline.coverage`, color = car_truck_van),alpha = 0.4)+theme_bw()+geom_hline(yintercept = mean_county,color='grey50')+ylab('Median Household Income')+xlab('Minimum Viable Coverage')+scale_x_continuous(labels = scales::percent)+scale_y_continuous(labels = function(x) paste0("$", x, 'k'))+scale_color_viridis_c(option = "plasma",labels = scales::percent)+theme(legend.position = 'none')

p3 <- ggplot(commuters) + geom_point(aes(y = car_truck_van, x = `NEVI.coverage`, color = car_truck_van),alpha = 0.4)+theme_bw()+geom_hline(yintercept = car_median,color='grey50')+ylab('percent car commuter')+xlab('Fast Charger Coverage')+scale_x_continuous(labels = scales::percent)+theme(axis.text.y=element_blank(),legend.position = 'none')+scale_color_viridis_c(option = "plasma",labels = scales::percent)

p4 <- ggplot(commuters) + geom_point(aes(y = Median_household_income/1000, x = `NEVI.coverage`, color = car_truck_van),alpha = 0.4)+theme_bw()+geom_hline(yintercept = mean_county,color='grey50')+ylab('')+xlab('Fast Charger Coverage')+scale_x_continuous(labels = scales::percent)+theme(axis.title.y=element_blank(),legend.position = 'none',axis.text.y=element_blank())+scale_color_viridis_c(option = "plasma",labels = scales::percent)

p5 <- ggplot(commuters) + geom_point(aes(y = car_truck_van, x = `AFC.coverage`, color = car_truck_van),alpha = 0.4)+theme_bw()+geom_hline(yintercept = car_median,color='grey50')+ylab('percent car commuter')+xlab('NEVI-program Coverage')+scale_x_continuous(labels = scales::percent)+scale_color_viridis_c(option = "plasma",labels = scales::percent)

p6 <- ggplot(commuters) + geom_point(aes(y = Median_household_income/1000, x = `AFC.coverage`, color = car_truck_van),alpha = 0.4)+theme_bw()+geom_hline(yintercept = mean_county, color='grey50')+ylab('')+xlab('AFCs Reach NEVI-Compliance')+scale_x_continuous(labels = scales::percent)+theme(axis.title.y = element_blank(), axis.text.y=element_blank(), legend.position = 'none')+scale_color_viridis_c('', option = "plasma",labels = scales::percent, limits = c(0, 1))
```


```{r}

(p2+p4+p6)+theme(legend.position = 'bottom')

```
```{r}
ggplot(commuters) + geom_point(aes(x = Median_household_income/1000, y = `Baseline.coverage`, colour = car_truck_van))+theme_bw()+geom_vline(xintercept = mean_county)+xlab('Median Household Income')+ylab('Minimum coverage')+scale_y_continuous(labels = scales::percent)+scale_x_continuous(labels = function(x) paste0("$", x, 'k'))+scale_colour_viridis_c(option = "plasma")#+ scale_colour_gradientn(colors=c("#fbfddf", "#e1e96b","#8da72a","#4E8E5B", "#0e758c"),limits = c(0,1))

ggplot(commuters) + geom_point(aes(x = Median_household_income/1000, y = `AFC.coverage`, colour = car_truck_van))+theme_bw()+geom_vline(xintercept = mean_county)+xlab('Median Household Income')+ylab('AFC coverage')+scale_y_continuous(labels = scales::percent)+scale_x_continuous(labels = function(x) paste0("$", x, 'k'))+
  scale_colour_viridis_c(option = "plasma",direction = -1)#scale_colour_gradientn(colors=c("red", "#e1e96b","#8da72a","#4E8E5B", "#0e758c"),limits = c(0,1))

ggplot(commuters) + geom_point(aes(x = Median_household_income/1000, y = `NEVI.coverage`, colour = car_truck_van))+theme_bw()+geom_vline(xintercept = mean_county)+xlab('Median Household Income')+ylab('Percent of Car Commuters')+scale_y_continuous(labels = scales::percent)+scale_x_continuous(labels = function(x) paste0("$", x, 'k'))+
  scale_colour_viridis_c(option = "plasma")#scale_colour_gradientn(colors=c("#fbfddf", "#e1e96b","#8da72a","#4E8E5B", "#0e758c"),limits = c(0,1))
```

```{r}

write.csv(st_drop_geometry(states), paste0(file.path, 'results/2023/', 'state_coverage_contiguous_tesla.csv'))
```